Project Light

### 2015-09-09 paper/paper.tex

- first background of our work, than alternative solutions

\subsection{Background}

- background:
	- "Standardized Protocol Stack..."\cite{palattella2013standardized} describes network stack for iot, maybe implemented in contiki
	- akes\cite{krentz15akes}
- related work:
	- webseite mit flickerer\cite{electricimp}
	- LiDSN\cite{doan2012lidsn}
	- message in a bottle\cite{kuo2007message}: init keys within Faraday cage, jam radio with outside device
	- Blink ’Em All\cite{saxena2009blink}: communication via light, but other way round: motes blink and camera parses it.
	- "Over the Air Provisioning..."\cite{chen2011over} uses eliptic curve crytpography, which needs a lot of space on the mote
	- smart sys tech 2015\cite{krentz20156doku}:
		- 6Doku protocol --> successor of sudoku protocol (diffie hellman, etc.)
		- touch-device with 6lowpan transmitter as (mother duck)
		- press butttons on motes and touchscreen on mother duck --> pair them
		-

\begin{itemize}
	\item LiDSN: A Method to Deploy Wireless Sensor Networks Securely based on light communication
	\item ...
\end{itemize}

>>>>

- IoT requires own network stack because of special needs: energy and resources, e.g. batteries should work for multiple years and mote memory will be very small (e.g. 48kb program flash for telosB mote CITE SOURCE), many addresses needed
- 6LowPan protocol stack as described in "Standardized protocol stack.." is tailoring this
- its using own implementations of layers, e.g. PHY for physical layer, and CoaP as applicationlayer as well as conventional ones (namely IPv6 as Internet layer) --> enables IoT

- there are some proposals for specialized security layers in this stack, e.g. akes \cite{krentz15akes}
- akes uses session keys and a neighborhood-exploration-technique to gain sufficient security level, even surviving reboots
- it still relies on predistributed keys on each mote
- how to predistribute in safe way?

\cite{chen2011over} proposes key provisioning without wiring using eliptic curve cryptography --> expensive for memory and energy.
- (own chips might solve this, but increase per unit cost)

\cite{kuo2007message} utilizes Faraday cage and another (third) radio jamming device for initialization.
-> requires special hardware

6doku \cite{krentz20156doku} proposes pairing with smartphone and extra-hardware for pairing
- extra hardware and motes need button

- some ideas to transmit keys via light:

- Blink 'Em All \cite{saxena2009blink} lets motes LEDs blink and computer with connected camera read it.

- LiDSN \cite{doan2012lidsn} same with special connector-hardware where mote gets put into. if mote has no led, light sensor is assumed and connector emits light. Proved as usable by end-user, but special hardware needed

- Electric Imp \cite{electricimp} sells proprietary BlinkUp technology: uses smart phone for flickering -> good for end users
- not scientifically examined till now (as far as we know)

thus, we propose a user-friendly wireless key provisioning protocols without additional hardware needed, just mote with light sensor and smart phone.
